Forecasting the 2024 U.S. Presidential Election

### 2024-10-21 paper/paper.qmd
some minor changed in cleaning section

Some variables were excluded for simplicity and relevance. For example, **population_full** and **answer** were dropped as they provided redundant or unnecessary information for this analysis. However, key variables like **pollster**, **pollscore**, **numeric grade**, and **sample size** were retained because they provide essential insights into the quality and precision of the polls, directly influencing the reliability of the models. These steps ensured the cleaned dataset was ready for analysis, with a focus on the most important predictors of voter support while minimizing extraneous information.

>>>>

Some variables were excluded for simplicity and relevance. For example, **"population_full"** and **"answer"** were dropped as they provided redundant or unnecessary information for this analysis. However, key variables like **"pollster"**, **"pollscore"**, **"numeric grade"**, and **"sample size"** were retained because they provide essential insights into the quality and precision of the polls, directly influencing the reliability of the models. These steps ensured the cleaned dataset was ready for analysis, with a focus on the most important predictors of voter support while minimizing extraneous information.
